---
title: "Group 45 CA pollution burden"
author: "Cristina Mancilla and Charlie Wilson"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r}
ces <- read_csv(here("data", "ces3demographics.csv" )) %>% 
  
  clean_names
```

```{r}
#Create a plot that uses point density to depict the relationship between percentage of white populaiton and CalEnviroScreen 3.0 

ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() + #create HEX plot
  labs(x = "Percentage (%) of white population", 
       y = "CalEnviroScreen 3.0 Score", 
       title = "Relationship between CalEnviroScreen 3.0 score and percentage (%) of white population ") +
  theme_minimal() + # update theme
  scale_fill_gradient(low = "darkblue", high = "red") # change colors to red and blue
```


**Figure 1**: Heat map shows the relationship between white communities (x-axis) in percentage (%) and the CalEnviroScreen 3.0 Score (y-axis). The CalEnviroScreen 3.0 score is a function of pollution burden and population characteristics. The color gradient indicates density of data points (CEJA Green Zones)"

There is a negative relationship between percent of white population and the CalEnviroScreen 3.0 score. As the percent of white population increases the CalEnviroScreen 3.0 score decreases as indicated by the color gradient. 





**Data Citation**: 
United States Census Bureau. 2010 Census.U.S. Census Bureau. 2010.
Office of
Environmental Health Hazard Assessment. CalEnviroScreen 3.0. 2018.